### 2020-10-27 doc/manuscript/Dow_manuscript.Rmd
draft growth_curves_all figure
#21

#Figure numbers
schematic=1 #illustrates parameters
growth_pheno_by_xylem = 2  #if we include more sites, we'll make this multi-panel
rel_growth = "2a" #Based on D'Orangeville Figure 3.a), but with relative growth
cum_growth = "2b" #Similar to D'Orangeville Figure 4.a), but with cumulative relative growth
climwin = 3
pheno_Tsensitivity = 4
model_summary = 5
DOYtiming = 6
DOYtiming_SCBI = "6a"
DOYtiming_Harvard = "6b"

@@

rel_growth_caption <- "Figure 2a. (SHOULD BE MERGED INTO SINGLE IMAGE WITH 2B. SEE BELOW FOR CAPTION)"
cum_growth_caption  <- "Figure 2. Growth trajectories for ring- and diffuse-porous trees, as both relative (a) and cumulative (b) fractions of total annual growth. Each line represents one year's growth for a given tree, fit with McMahon model."

@@

Growth pheonology differed between ring- and diffuse- porous species, with ring-porous species having an earlier start to growth, with growth spread out over a longer growing season (Fig. `r growth_pheno_by_xylem`).
For ring-porous trees, on average, 25% of annual growth was achieved on **April 23** ($DOY_{25}$=**113**), 50% on **May 27** ($DOY_{50}$=**147**), and 75% on **June 30** ($DOY_{75}$=**181**), for an average peak growing season length of **68** days. Maximum growth rate occurred *on $DOY_{50}$* and averaged .048 **mm day^-1^ (?)**. 
For diffuse-porous trees, on average, 25% of annual growth was achieved on **June 2** ($DOY_{25}$=**153**), 50% on **June 20** ($DOY_{50}$=**171**), and 75% on **July 9** ($DOY_{75}$=**190**), for an average peak growing season length of **37** days. Maximum growth rate occurred *just one day after $DOY_{50}$* on **June 21** ($DOY_{max}$=**172**) and averaged .068 **mm day^-1^ (?)**.

@@

```{r rel_growth, out.width="100%", echo=FALSE, fig.align="center", fig.cap= rel_growth_caption}
# Created in RScripts/additional_figures.R
knitr::include_graphics("tables_figures/rel_growth.png")
```

```{r cum_growth, out.width="100%", echo=FALSE, fig.align="center", fig.cap= cum_growth_caption}
# Created in RScripts/additional_figures.R
knitr::include_graphics("tables_figures/cum_growth.png")
```

@@

This analysis is one of a first generation of intraannual dendroband tree growth studies, and as such, is only the tip of the ice berg. Here, we focused our analysis purely on early Spring warming. This falls short of the reality of our changing climate, where each season is being affected in some way, leading to a combination of stressors on plant growth. For example, diffuse porous trees seemed to show little, if any, relationship with the climate window defined here, but if we shift that window forward 20 days, the effect increases dramatically, signalling a greater importance of May/June TMAX on trees of that wood type (figure or table?). This revelation agrees with the results from other climate sensitivity studies like Helcoski et al (2019), which found differences in interspecific growth responses to several climate variables throughout the year. Additionally, Other studies have found that Autumn leaf senescence is being delayed in response to warmer temperatures in the previous year's Winter or Autumn (), positive correlation between growth and higher winter temperatures (Heide, 1993; Delpierre et al, 2009), stunted total productivity induced by drought and high TMAX in the current year's Summer (), and an increase in diffuse-porous tree growth during the gorwing season following an abnormally cold winter (Benito & Pederson, 2015; Elliot et al, 2015). How these relationships may impact intraannual growth patterns is uncertain, but identifying such relationships will help us further understand how climate change is impacting forests.

@@

>>>>

#Figure numbers
schematic=1 #illustrates parameters
growth_curves_all = 2  
    rel_growth_SCBI = "2a" 
    rel_growth_HF = "2b" 
    cum_growth_SCBI = "2c" 
    cum_growth_HF = "2d" 
climwin = 3
pheno_Tsensitivity = 4
model_summary = 5
DOYtiming = 6
DOYtiming_SCBI = "6a"
DOYtiming_Harvard = "6b"

@@

growth_curves_all_caption  <- "Figure 2. Growth trajectories for ring- and diffuse-porous trees, as both relative and cumulative fractions of total annual growth. Each line represents one year's growth for a given tree, fit with McMahon model."

@@

Growth pheonology differed between ring- and diffuse- porous species, with ring-porous species having an earlier start to growth, with growth spread out over a longer growing season (Fig. `r growth_curves_all`).
For ring-porous trees, on average, 25% of annual growth was achieved on **April 23** ($DOY_{25}$=**113**), 50% on **May 27** ($DOY_{50}$=**147**), and 75% on **June 30** ($DOY_{75}$=**181**), for an average peak growing season length of **68** days. Maximum growth rate occurred *on $DOY_{50}$* and averaged .048 **mm day^-1^ (?)**. 
For diffuse-porous trees, on average, 25% of annual growth was achieved on **June 2** ($DOY_{25}$=**153**), 50% on **June 20** ($DOY_{50}$=**171**), and 75% on **July 9** ($DOY_{75}$=**190**), for an average peak growing season length of **37** days. Maximum growth rate occurred *just one day after $DOY_{50}$* on **June 21** ($DOY_{max}$=**172**) and averaged .068 **mm day^-1^ (?)**.

@@

```{r growth_curves_all, out.width="100%", echo=FALSE, fig.align="center", fig.cap= growth_curves_all_caption}
# Created in RScripts/additional_figures.R
knitr::include_graphics("tables_figures/growth_curves_all.png")
```

@@

This analysis is one of a first generation of intraannual dendroband tree growth studies, and as such, is only the tip of the ice berg. Here, we focused our analysis purely on early Spring warming. This falls short of the reality of our changing climate, where each season is being affected in some way, leading to a combination of stressors on plant growth. For example, diffuse porous trees seemed to show little, if any, relationship with the climate window defined here, but if we shift that window forward 20 days, the effect increases dramatically, signalling a greater importance of May/June TMAX on trees of that wood type (figure or table?). This revelation agrees with the results from other climate sensitivity studies like Helcoski et al (2019), which found differences in interspecific growth responses to several climate variables throughout the year. Additionally, Other studies have found that Autumn leaf senescence is being delayed in response to warmer temperatures in the previous year's Winter or Autumn (), positive correlation between growth and higher winter temperatures (Heide, 1993; Delpierre et al, 2009), stunted total productivity induced by drought and high TMAX in the current year's Summer (), and an increase in diffuse-porous tree growth during the growing season following an abnormally cold winter (Benito & Pederson, 2015; Elliot et al, 2015). How these relationships may impact intraannual growth patterns is uncertain, but identifying such relationships will help us further understand how climate change is impacting forests.

@@

Geng et al. 2020 GCB- Climate warming increases spring phenological differences among temperate trees.
